---
title: "R Notebook"
output: html_notebook
author: "Ryan Willett"
---

```{r, echo=FALSE, warning=F}
library(tidyverse)
library(ggplot2)
library(igraph)
library(sigmaNet)
library(scales)
library(RSQLite)
library(DBI)


```

```{r}
con <- dbConnect(RSQLite::SQLite(), "kolDB.db")

dbListTables(con)
```

```{r}
metricsDF <- dbGetQuery(con, "SELECT * FROM metrics;")
el_df <- dbGetQuery(con, "SELECT author1,author2 FROM  edgelist_clean;")
```


```{r}
el_df <- read.csv("airqualEL.csv")
```



```{r}
authors_graph <- graph_from_data_frame(el_df, directed=F)
```

```{r}
V(authors_graph)$degree <- degree(authors_graph)
```

```{r}
degree(authors_graph) %>% sort(decreasing = T) %>% head(20)
```

The degree distribution is a classic scale-free network
```{r}
degDF <- data.frame(name = V(authors_graph)$name, degree = V(authors_graph)$degree)

ggplot(degDF, aes(degree)) + geom_histogram(binwidth = 19) + 
  labs(x="Degree Frequency", y="Number of Coauthors", title="Degree Distribution of Coauthorship in the Air Quality Field") + 
  theme_classic()


ggplot(degDF, aes(degree)) + geom_freqpoly(binwidth = 19, fill="black") + xlim(0,500) + 
  labs(x="Degree Frequency", y="Number of Coauthors", title="Degree Distribution of Coauthorship in the Air Quality Field (Zoom)") + 
  theme_classic()
```


################# WORKING WITH A SUBGRAPH OF MORE HIGHLY CONNECTED AUTHORS ##################################

Paring down the network to the highly connected subgraph (those with > 500 coauthors)
```{r}
authors_graph_trim <- delete_vertices(authors_graph, V(authors_graph)[degree<500])
```

Calculates the graph layout for the subgraph (This one is Kamada-Kawaii)
```{r}
# fr_sub <- layout_with_fr(authors_graph_trim)
kk_sub <- layout_with_kk(authors_graph_trim)
```

Simplifies the graph and runs a quick clustering algorithm on the subgraph (prunes edges to self)
```{r}
authors_graph_trim2 <- simplify(authors_graph_trim, remove.multiple = T, remove.loops = T)
V(authors_graph_trim)$clust <- membership(cluster_fast_greedy(authors_graph_trim2))
```

This would be how you plot this network, but for this current example network, it takes a long time to plot (too many nodes)
```{r}
# sig_trim_kk <- sigmaFromIgraph(authors_graph_trim, layout = kk_sub) #%>%
#   addNodeSize(sizeVector = V(authors_graph_trim)$degree, maxSize = 8) %>% #sizeMetric = 'degree', maxSize = 8) %>%
#   addNodeLabels(labelAttr = 'label') %>%
#   addNodeColors(colorAttr = 'clust') %>%
#   addEdgeSize(sizeAttr = "degree", minSize = 0.1, maxSize = 2.5)
# sig_trim_kk
```







```{r}

# Input the name of a node and the function calculates several centrality measures of the 1.5 egocentric network
ego_profile <- function(x, g){
  ego_graph <- make_ego_graph(g, order=1, x, mindist = 0)[[1]] # Takes the subgraph of the target node to an order of 1
  ego_graph <- simplify(ego_graph, remove.loops = T, remove.multiple = T)
  ego_density <- edge_density(ego_graph) # Calculates the density of the subgraph
  deg <- V(g)[x]$degree # Assigns the degree value for the target "ego" node
  ave_path <- average.path.length(ego_graph) # Calculates average path within the subgraph
  eigen <- eigen_centrality(ego_graph, directed = F)$value # Calculates eigenvector centrality
  btw <- mean(betweenness(ego_graph))
  close <- mean(closeness(ego_graph, mode = 'all'))
  
  centralities <- c(ego_density, deg, ave_path, eigen, btw, close)
  
  names(centralities) <- c("ego_density", 'degree', 'ave_pathlength', 'eigenvector_cent', 'betweenness', 'closeness')
  
  return(centralities)
}

x_nodes <- function(g, v1, v2) {
  # Input a graph and 2 nodes and it will return a list of nodes that are shared neighbors
  n.v1 <- neighbors(g, as.numeric(V(g)[v1]))
  n.v2 <- neighbors(g, as.numeric(V(g)[v2]))
  
  x_v <- intersection(n.v1, n.v2)
  
  return(x_v)
}

```

This outputs a variety of centrality measures of the 1.5 ego network subgraph for the target node.
```{r}
ego_profile("L Mitchell", authors_graph)
```

```{r}
inspect_ego <- function(node_name){
  # prof <- ego_profile(node_name, authors_graph)
  print("Extracting subgraph")
  
  ego_graph <- make_ego_graph(authors_graph, order=1, node_name, mindist = 0)[[1]]
  
  ego_graph <- simplify(ego_graph, remove.loops = T, remove.multiple = T)
  V(ego_graph)$clust <- membership(cluster_fast_greedy(ego_graph))
  
  print("Calculating graph layout")
  
  kk_ego <- layout_with_kk(ego_graph)
  
  sig_ego <- sigmaFromIgraph(ego_graph, layout = kk_ego) %>%
  addNodeSize(sizeVector = V(ego_graph)$degree, maxSize = 8) %>% 
  #addNodeLabels(labelAttr = 'label') %>%
  addNodeColors(colorAttr = 'clust') %>% 
  addEdgeSize(oneSize = 0.1)
  return(sig_ego)
}

ego_export <- function(node_name, fileOut){
  signet_obj <- inspect_ego(node_name)
  signet_obj %>% saveSigma(fileOut)
}
```

This provides the plot of the 1.5 ego network graph 
```{r}
inspect_ego("L Mitchell")
```

This saves the 1.5 egonetwork of the input node name
```{r}
ego_export("L Mitchell", "lmitchell.html")
```

